Impact ionization processes in a photodriven Mott insulator: influence of phononic dissipation

### 2022-08-30 Paper1.tex
Last version paper 30.08.2022
Smoothened formulations in text and footnotes. Moved fig. 8 to bottom of page. Altered fig. 1 slightly to contain Gamma_l and Gamma_r, not Gamma. Renamed energy scale to t_{resc}.

\newcommand{\mscomm}[1]{{\color{blue} MS Comment: #1}}
%\newcommand{\kh}[1] {\textcolor{green}{KH comment: #1}}

@@

%EA
\title{Impact ionization processes in a photodriven Mott insulator: influence of phononic dissipation}

@@

As a scattering process, II competes with electron-phonon (e-ph) scattering which is the dominant relaxation mechanism in conventional semiconductors. This may not be the case in Mott insulators, at least in certain cases ~\cite{co.ma.14}. Therefore, it is essential to understand the influence of e-ph scattering on the photocurrent and II in Mott photovoltaic devices, which is the issue we address in this paper.

@@

\begin{figure}[b] 
% \captionsetup{width=\textwidth} 
\includegraphics[width=0.9\linewidth]{./figures_Paper1/setup_voltmeter.pdf}
\caption{(Color online) Schematic representation of the setup. A central, correlated layer with local Hubbard interaction $U$ and e-ph coupling $g$ (green) is sandwiched between two non-interacting layers (red) via the hybridization $v$ (black). The latter are in turn coupled to wide-band fermion reservoirs (blue) with different chemical potentials $\mu_{\text{l}/\text{r}}$, which introduce a broadening $\Gamma=\Gamma_{\text{l}}=\Gamma_{\text{r}}$.}
\label{fig:setup}
\end{figure}

@@

Our setup introduced in Sec.~\ref{sec:intro} and shown in Fig.~\ref{fig:setup} is described by the Hamiltonian
%
\begin{equation}
\label{eq:Hamiltonian}
\begin{split} 
\hat{H}(t)&=\varepsilon_{\text{c}} \sum_{i\sigma}\hat{n}_{i\sigma} -\sum_{\sigma}\sum_{(i,j)} t_{ij}(t) \hat{c}^{\dagger}_{i\sigma} \hat{c}_{j\sigma}
\\ & + U \sum_{i} \hat{n}_{i\uparrow} \hat{n}_{i\downarrow}+\hat{H}_{\text{e-ph}} + \hat{H}_{\text{ph}}+\hat{H}_{\text{lead}}.
\end{split}
\end{equation}
% 
The operator $\hat{c}^{\dagger}_{i\sigma}$ ($\hat{c}_{i\sigma}$) creates (annihilates) a particle with spin $\sigma= \lbrace \uparrow,\downarrow \rbrace$ on the $i$-th lattice site and $\hat{n}_{i\sigma}\equiv \hat{c}^{\dagger}_{i\sigma} \hat{c}_{i\sigma}$ is the particle number operator. We denote with $(i,j)$ the sum over nearest-neighbor sites and with $\varepsilon_{\text{c}} \equiv -U/2$ the on-site energy. The driving field consists of a time-periodic, homogeneous and monochromatic electric field with frequency $\Omega$. In the temporal gauge it enters via the Peierls substitution in the time-dependent hopping in Eq.~\eqref{eq:Hamiltonian}~\cite{peie.33}

\begin{equation}\label{eq:peierls} 
t_{ij}(t) = t_{\text{c}} \ e^{-\ii \frac{q}{\hbar} \left( \vec{r}_j - \vec{r}_i \right) \cdot \vec{A}(t)}, 
\end{equation}
% 
where $t_{\text{c}}$ is the intra-layer hopping, $\vec{A}$(t) the time-dependent vector potential, $\hbar$ Planck's constant and $q$ the charge of the electrons. Following Refs.~\cite{ts.ok.08,mu.we.18}, we choose for simplicity
 $\vec{A}(t)=\vec{e}_{0} A(t)$, which points along the 
lattice body diagonal $\vec{e}_{0}=(1,1,\dots,1)$.  $A(t)=\frac{\hbar}{qa}\aamp\sin(\Omega t)$ with $\aamp=-\frac{qE_0a}{\hbar\Omega}$,  $E_0$ is the  electric field amplitude, and $a$ the lattice spacing ~\cite{ts.ok.08}. 
In this temporal gauge the electric field is $\vec{E}= -\partial_{t}\vec{A}(t) = \vec{e}_{0}E_0 \cos(\Omega t)$.

@@

Within the remainder of this paper we choose our units so that  $\hbar = k_{\text{B}} = a = 1 = -q$, $t^{\ast}=2\sqrt{2}$ ~\footnote{With such choice for $t^{\ast}$ we reproduce the DOS of a 2D layer with $t_{\text{c}}=1$  in order to compare with Ref.~\cite{so.do.18}.}, and $t_r \equiv \frac{t^{\ast}}{2\sqrt{2}}=1$ as unit of energy.

@@

For completeness, we now
 briefly describe the self-consistent F-DMFT scheme used.
(i) We start from an initial guess for the electron SE $\kel{\mat{\Sigma}}(\omega)$ and set $\kel{\mat \Sigma}_{\text{e-ph}}(\omega)=0$. (ii) Then we compute the local electron GF as 
%  
\begin{equation}\label{eq:Lat_LocGF}
\begin{split}
\kel{\mat G}_{\text{loc}}(\omega) &= \int \dd\epsilon \int \dd\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \times \\ 
&\times \left[\kel{\mat G}^{-1}_{0}(\omega,\epsilon,\overline{\epsilon}) - \kel{\mat\Sigma}(\omega) - \kel{\mat \Sigma}_{\text{e-ph}}(\omega) \right]^{-1}.
\end{split}
\end{equation}
% 
(iii) Using Eq.~\eqref{eq:backbone_e-ph_SE}, we obtain the phonon contribution to the SE $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$.
(iv) The problem is mapped onto a single impurity plus bath, whose hybridization function
is given by
%
\begin{equation}\label{eq:imp_Dyson_eq}
\kel{\mat{\Delta}}(\omega) = \kel{\mat{g}}^{-1}_{0,\text{site}}(\omega) - \kel{\mat{G}}^{-1}_{\text{loc}}(\omega) - \kel{\mat{\Sigma}}(\omega),
\end{equation}   
%  
where $\kel{\mat{g}}^{-1}_{0,\text{site}}(\omega)$ is defined as in Eq.~\eqref{eq:inv_non-int_lat_GF_comps} with $\varepsilon_{mn}(\epsilon,\overline{\epsilon})=0$. (v) The nonequilibrium many-body impurity problem is solved according to the procedure described below, leading to the new $\kel{\mat{\Sigma}}(\omega)$. (vi) We insert the electron and e-ph SEs into step (ii) and iterate the steps (ii)-(vi) until convergence.

Eq.~\eqref{eq:imp_Dyson_eq} gives a bath hybridization function $\kel{\mat\Delta}(\omega)$ whose periodic time-dependence is encoded in its Floquet structure. 
This means that, in principle, one should solve a time-periodic impurity problem leading to a non-diagonal SE. However, in Ref.~\cite{so.do.18} it was argued and shown that for the considered electric field amplitudes, off-diagonal terms in the electron SE $\kel{\mat{\Sigma}}(\omega)$ can be safely neglected with respect to the diagonal ones. We follow this argument and adopt here 
this Floquet-diagonal self-energy approximation (FDSA) as well. In addition, it turns out that also for the 
 phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified~\footnote{More specifically, we verified that in the parameters range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ are orders of magnitude smaller than the diagonal ones}. 
Consequently, we  solve a nonequilibrium stationary impurity problem, by considering only the $(0,0)$-Floquet matrix element of all the quantities in Eq.~\eqref{eq:imp_Dyson_eq}. The other diagonal components of the SEs are then reconstructed by using the property $\kel{\Sigma}_{mm}(\omega) = \kel{\Sigma}_{00}(\omega+m\Omega)$.

@@

In order to study II in a Mott insulating layer, we adjust the bands to achieve the energy scheme shown in Fig.~\ref{fig:energy_setup}(a). 
 We follow Ref.~\cite{so.do.18} and take $U=12$ and unless stated otherwise $E_0=2$. The fermion leads and the acoustic phonons have temperature $T=0.02$. We consider a particle-hole symmetric system with $\Gamma_{\text{l}}=\Gamma_{\text{r}}=0.37$, $t_{\text{l}}=t_{\text{r}}=1.7$, $\varepsilon_{\text{l}/\text{r}}=\mp 6$ and $v_{\text{l}}=v_{\text{r}}=v$. The parameters $t_{\text{l/r}}$, $\varepsilon_{\text{l/r}}$, and  $\Gamma_{\text{l/r}}$ are chosen such that the leads' DOS approximately overlaps with the Hubbard bands, i.e. they exhibit a \textquoteleft bandwidth\textquoteright~\footnote{Notice that the support of its spectrum is formally infinite. $W_{\text{b}}$ is the value at which the spectrum gets  suppressed.} $W_{\text{b}}\approx 8$ and are centered at the same position. The chemical potentials are set to $\mu_{\text{l}/\text{r}} =\mp 1$, so that a current from left to right is produced by taking energy from the driving.

Due to the hybridization with the leads, the local DOS of the Hubbard layer only features a pseudogap
 $\Delta_{\text{pg}} \approx 4$.
All simulations are carried out with the dimensionless factor $\alpha\equiv t_{r}E_0/\Omega^{2}<0.5$ for which the FDSA is justified~\footnote{In Ref.~\cite{so.do.18} the factor is defined as $\alpha=t_{c}E_0/\Omega^{2}$ and $t_{\text{c}}=1$. Setting $t_{r}=1$, we define for consistency $\alpha$ as in the main text.}. Whenever the electron-phonon interaction is included, we take $g=0.8$ and unless stated otherwise $\omega_{\text{ph}}=0.1$.

@@

\begin{itemize}
\item For $\Omega<\Delta_{\text{pg}}$, 
we expect a strong suppression of the current~\footnote{The remaining leak current can be either produced by multiple-photon absorption processes, which however, are strongly suppressed, or by the fact that there is no true gap} and
we do not expect any current if the DOS of the correlated layer has a true gap.
\item For $\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$ as shown in Fig.~\ref{fig:energy_setup}(b), an electron coming from the left lead into the LHB is photoexcited to the UHB and can escape directly into the right lead without additional scattering.  Such processes are often referred to as direct excitations (DEs).
\item For $2\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$ as shown in Fig.~\ref{fig:energy_setup}(c), a photoexcited electron in the UHB can excite via II a second electron from LHB to UHB, before both escape into the right lead.
\item For $\Omega>\Delta_{\text{pg}}+2W_{\text{b}}$, there are no final states available for a photoexcited electron and we do not expect the transition to occur. 
\end{itemize}

Notice that in the energy window $\Delta_{\text{pg}}<\Omega<2\Delta_{\text{pg}}$ the only scattering processes taking place are DEs, while for $2\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$, both DE and II can occur. 
This is in contrast to the case of Ref.~\cite{so.do.18}, in which the peculiar ad-hoc narrow leads' bands only allow for II processes in a certain $\Omega$-range.
For this reason, and due to the fact that the boundaries of these energy ranges are not strict, it is more tricky to disentangle these physical processes in the present case.

@@

Upon inclusion of e-ph scattering, the outlined scheme remains valid except for the fact that  the pseudogap $\Delta_{\text{pg}}$ is slightly modified. As shown in Sec.~\ref{sec:E0_2_electrons_phonons}, the phonons broaden the DOS of the correlated layer and slightly fill and shrink the pseudogap.

% \onecolumngrid
\begin{figure*}[t]
\includegraphics[width=0.7\textwidth]{./figures_Paper1/j_vs_omega_mu1_v_0.4_0.8_eph.pdf}
% \captionsetup{width=\textwidth}
\caption{(Color online) 
 (a) Time-averaged steady-state current $j$ and (b) double occupancy $N_{\text{D}}$ plotted as a function of the driving frequency $\Omega$. Results are shown for different values of the lead-layer hybridization $v$ as well as without and with e-ph interaction.
 Default parameters are specified at the beginning of Sec.~\ref{sec:results}.} 
\label{fig:j_vs_omega_mu1_v_0.4_0.8_eph}
\end{figure*}
% \twocolumngrid

@@

\begin{figure}[b] 
% \captionsetup{width=\textwidth}   
\includegraphics[width=\linewidth]{./figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_5_11_e.pdf}
\caption{(Color online) Spectral function $A(\omega)$ (solid line) and occupation function $N(\omega)$ (shaded area) at (a) $\Omega=5$ and (b) $\Omega=11$ for $v=0.4$ and $0.8$ for the EO system. Default parameters are specified at the beginning of Sec.~\ref{sec:results}.}
\label{fig:spec_filling_mu1_v_0.4_0.8_O_5_11_e}
\end{figure}

\begin{figure}[b]  
% \captionsetup{width=\textwidth} 
\includegraphics[width=\linewidth]{./figures_Paper1/j_vs_omega_mu1_v_0.8_e_E0_3_4.pdf} 
\caption{(Color online) (a) Time-averaged steady-state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, at $v=0.8$ for $E_0=3,4$ for the EO system. Default parameters are specified at the beginning of Sec.~\ref{sec:results}.} 
\label{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4}
\end{figure}

For $\Omega\gtrsim8$, the current increases further until it reaches its peak at $\Omega\approx 11$.
In this range both DE and II can occur in principle. The height of the peak is approximately the same for both $v$, despite they differ by a factor of two. The double occupation in this range shows a similar behavior as the current for $v=0.4$ with a peak around $\Omega\approx 11$, while it exhibits a plateau for $v=0.8$. For $v=0.4$ the current curve is characterized by a substantial increase in slope around $\Omega \approx 7$, which cannot be observed for $v=0.8$. This, together with the comparable magnitude of the current maxima at $\Omega\approx 11$ and the behavior of the double occupation strongly suggests that for $v=0.4$ a substantial rate of II processes take place, while these are absent or negligible for $v=0.8$.
Here,  the plateau in $N_{\text{D}}$ for $v=0.8$ suggests that photoexcited electrons arriving in the UHB quickly escape to the right fermionic lead and do not have time to induce II processes.

@@

This behavior is influenced by the  electric field amplitude $E_0$  as illustrated in Fig.~\ref{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4}(a). For $E_0=4$ the current develops a sudden increase in slope around $\Omega\approx7$ as well as a pronounced peak around $\Omega\approx 11$ for the larger hybridization $v=0.8$. This feature starts developing already at $E_0=3$. This tendency, corroborated by the behavior of the double occupation displayed in Fig.~\ref{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4}(b), suggests an  important role of II also for larger values of $v$, provided the field amplitude is strong enough.

@@

The double occupation $N_{\text{D}}$  shown in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b) is larger than and follows the behavior of its EO counterpart within the entire $\Omega$-range considered.
The spectral and occupation functions  shown in Fig.~\ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph} display a redistribution of spectral weight from the peaks towards the edges of the bands, thus reducing the pseudogap. Consequently, the occupation of positive energy states is slightly shifted to the bottom of the UHB compared to the EO case, as the occupation function shows.
 The spectral function in presence of phonons is  broadened and tends to fill the pseudogap $\Delta_{\text{pg}}$ as anticipated in Sec.~\ref{sec:scheme_electrons_phonons}.
This reduction of the pseudogap explains why the current in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a) is slightly larger in presence of phonons for $\Omega\lesssim7$. With a smaller pseudogap and more states at its edges, more electrons can be directly excited with a given driving frequency $\Omega$ thereby increasing the photocurrent. On the other hand, the suppression of the current by e-ph interaction in the range $7\lesssim\Omega\lesssim14$ is due to the dissipation-induced reduction of spectral weight at frequencies $|\omega| \gtrsim 3.5$, cf. Fig. \ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}.

\begin{figure}[b]
% \captionsetup{width=\textwidth} 
\includegraphics[width=\linewidth]{./figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_11_eph.pdf}
\caption{(Color online) Spectral function $A(\omega)$ (solid line) and occupation function $N(\omega)$ (shaded area) at $\Omega=11$ without and with e-ph interaction, for (a) $v=0.4$ and (b) $v=0.8$. Default parameters are specified at the beginning of Sec.~\ref{sec:results}.} 
\label{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}
\end{figure}

@@

\begin{figure}[t] 
% \captionsetup{width=\textwidth}  
\includegraphics[width=\linewidth]{./figures_Paper1/j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph.pdf}
\caption{(Color online) (a) Time-averaged steady-state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, for $v=0.4, 0.8$, at phonon cutoff frequencies $\omega_{\text{ph}}=0.025, 0.05$. Default parameters are specified at the beginning of Sec.~\ref{sec:results}.} 
\label{fig:j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph}
\end{figure}

@@

% \bibliographystyle{/afs/itp.tugraz.at/user/arrigoni/noneq-group/bibtex/prsty} 
%\bibliography{New_References,/afs/itp.tugraz.at/user/arrigoni/noneq-group/bibtex/references_database.bib}
% \bibliography{Additional_Refs.bib,references_database.bib}
%\bibliography{New_References,references_database.bib}

>>>>

@@

\title{Impact ionization processes in a photodriven Mott insulator: influence of phononic dissipation}

@@

As a scattering process, II competes with electron-phonon (e-ph) scattering which is the dominant relaxation mechanism in conventional semiconductors. This may not be the case in Mott insulators, at least in certain cases~\cite{co.ma.14}. Therefore, it is essential to understand the influence of e-ph scattering on the photocurrent and II in Mott photovoltaic devices, which is the issue we address in this paper.

@@

\begin{figure}[b] 
\includegraphics[width=0.9\linewidth]{./figures_Paper1/setup_voltmeter.pdf}
\caption{(Color online) Schematic representation of the setup. A central, correlated layer with local Hubbard interaction $U$ and e-ph coupling $g$ (green) is sandwiched between two non-interacting layers (red) via the hybridization $v$ (black). The latter are in turn coupled to wide-band fermion reservoirs (blue) with different chemical potentials $\mu_{\text{l}/\text{r}}$, which introduce broadenings $\Gamma_{\text{l}/\text{r}}$.}
\label{fig:setup}
\end{figure}

@@

Our setup introduced in Sec.~\ref{sec:intro} and shown in Fig.~\ref{fig:setup} is described by the Hamiltonian
%
\begin{equation}
\label{eq:Hamiltonian}
\begin{split} 
\hat{H}(t)&=\varepsilon_{\text{c}} \sum_{i\sigma}\hat{n}_{i\sigma} -\sum_{\sigma}\sum_{(i,j)} t_{ij}(t) \hat{c}^{\dagger}_{i\sigma} \hat{c}_{j\sigma}
\\ & + U \sum_{i} \hat{n}_{i\uparrow} \hat{n}_{i\downarrow}+\hat{H}_{\text{e-ph}} + \hat{H}_{\text{ph}}+\hat{H}_{\text{lead}}.
\end{split}
\end{equation}
% 
The operator $\hat{c}^{\dagger}_{i\sigma}$ ($\hat{c}_{i\sigma}$) creates (annihilates) an electron with spin $\sigma= \lbrace \uparrow,\downarrow \rbrace$ on the $i$-th lattice site and $\hat{n}_{i\sigma}\equiv \hat{c}^{\dagger}_{i\sigma} \hat{c}_{i\sigma}$ is the particle number operator. We denote with $(i,j)$ the sum over nearest-neighbor sites and with $\varepsilon_{\text{c}} \equiv -U/2$ the on-site energy. The driving field consists of a time-periodic, homogeneous and monochromatic electric field with frequency $\Omega$. In the temporal gauge it enters via the Peierls substitution in the time-dependent hopping in Eq.~\eqref{eq:Hamiltonian}~\cite{peie.33}

\begin{equation}\label{eq:peierls} 
t_{ij}(t) = t_{\text{c}} \ e^{-\ii \frac{q}{\hbar} \left( \vec{r}_j - \vec{r}_i \right) \cdot \vec{A}(t)}, 
\end{equation}
% 
where $t_{\text{c}}$ is the intra-layer hopping, $\vec{A}$(t) the time-dependent vector potential, $\hbar$ Planck's constant and $q$ the charge of the electrons. Following Refs.~\cite{ts.ok.08,mu.we.18}, we choose for simplicity
 $\vec{A}(t)=\vec{e}_{0} A(t)$, which points along the 
lattice body diagonal $\vec{e}_{0}=(1,1,\dots,1)$. Therein $A(t)=\frac{\hbar}{qa}\aamp\sin(\Omega t)$ with $\aamp=-\frac{qE_0a}{\hbar\Omega}$, $E_0$ is the electric field amplitude, and $a$ the lattice spacing~\cite{ts.ok.08}. 
In this temporal gauge the electric field is $\vec{E}= -\partial_{t}\vec{A}(t) = \vec{e}_{0}E_0 \cos(\Omega t)$.

@@

Within the remainder of this paper we choose our units so that  $\hbar = k_{\text{B}} = a = 1 = -q$, $t^{\ast}=2\sqrt{2}$~\footnote{With such choice for $t^{\ast}$ we reproduce the DOS of a 2D layer with $t_{\text{c}}=1$  in order to compare with Ref.~\cite{so.do.18}.}, and $t_{\text{resc}} \equiv \frac{t^{\ast}}{2\sqrt{2}}=1$ as unit of energy.

@@

For completeness, we now briefly describe the self-consistency F-DMFT scheme used.
(i) We start from an initial guess for the electron SE $\kel{\mat{\Sigma}}(\omega)$ and set $\kel{\mat \Sigma}_{\text{e-ph}}(\omega)=0$. (ii) Then we compute the local electron GF as 
%  
\begin{equation}\label{eq:Lat_LocGF}
\begin{split}
\kel{\mat G}_{\text{loc}}(\omega) &= \int \dd\epsilon \int \dd\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \times \\ 
&\times \left[\kel{\mat G}^{-1}_{0}(\omega,\epsilon,\overline{\epsilon}) - \kel{\mat\Sigma}(\omega) - \kel{\mat \Sigma}_{\text{e-ph}}(\omega) \right]^{-1}.
\end{split}
\end{equation}
% 
(iii) Using Eq.~\eqref{eq:backbone_e-ph_SE}, we obtain the phonon contribution to the SE $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$.
(iv) The problem is mapped onto a single impurity plus bath, whose hybridization function
is given by
%
\begin{equation}\label{eq:imp_Dyson_eq}
\kel{\mat{\Delta}}(\omega) = \kel{\mat{g}}^{-1}_{0,\text{site}}(\omega) - \kel{\mat{G}}^{-1}_{\text{loc}}(\omega) - \kel{\mat{\Sigma}}(\omega),
\end{equation}   
%  
where $\kel{\mat{g}}^{-1}_{0,\text{site}}(\omega)$ is defined as in Eq.~\eqref{eq:inv_non-int_lat_GF_comps} with $\varepsilon_{mn}(\epsilon,\overline{\epsilon})=0$. (v) The nonequilibrium many-body impurity problem is solved according to the procedure described below, leading to the new $\kel{\mat{\Sigma}}(\omega)$. (vi) We insert the electron and e-ph SEs into step (ii) and iterate the steps (ii)-(vi) until convergence.

Eq.~\eqref{eq:imp_Dyson_eq} gives a bath hybridization function $\kel{\mat\Delta}(\omega)$ whose periodic time-dependence is encoded in its Floquet structure. 
This means that, in principle, one should solve a time-periodic impurity problem leading to a non-diagonal SE. However, in Ref.~\cite{so.do.18} it was argued and shown that for the considered electric field amplitudes, off-diagonal terms in the electron SE $\kel{\mat{\Sigma}}(\omega)$ can be safely neglected with respect to the diagonal ones. We follow this argument and adopt here 
this Floquet-diagonal self-energy approximation (FDSA) as well. In addition, it turns out that also for the 
 phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified~\footnote{More specifically, we verified that in the parameter range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ are at least two orders of magnitude smaller than the diagonal ones}. 
Consequently, we  solve a nonequilibrium stationary impurity problem, by considering only the $(0,0)$-Floquet matrix element of all the quantities in Eq.~\eqref{eq:imp_Dyson_eq}. The other diagonal components of the SEs are then reconstructed by using the property $\kel{\Sigma}_{mm}(\omega) = \kel{\Sigma}_{00}(\omega+m\Omega)$.

@@

In order to study II in a Mott insulating layer, we adjust the bands to achieve the energy scheme shown in Fig.~\ref{fig:energy_setup}(a). 
 We follow Ref.~\cite{so.do.18} and take $U=12$ and unless stated otherwise $E_0=2$. The fermion leads and the acoustic phonons have temperature $T=0.02$. We consider a particle-hole symmetric system with $\Gamma_{\text{l}}=\Gamma_{\text{r}}=0.37$, $t_{\text{l}}=t_{\text{r}}=1.7$, $\varepsilon_{\text{l}/\text{r}}=\mp 6$ and $v_{\text{l}}=v_{\text{r}}=v$. The parameters $t_{\text{l/r}}$, $\varepsilon_{\text{l/r}}$, and  $\Gamma_{\text{l/r}}$ are chosen such that the leads' DOS approximately overlaps with the Hubbard bands, i.e. they exhibit a \textquoteleft bandwidth\textquoteright~\footnote{Notice that the support of the leads' spectra are formally infinite. $W_{\text{b}}$ is the value at which the spectrum gets  suppressed.} $W_{\text{b}}\approx 8$ and are centered at the same position. The chemical potentials are set to $\mu_{\text{l}/\text{r}} =\mp 1$, so that a current from left to right is produced by taking energy from the driving.

Due to the hybridization with the leads, the local DOS of the Hubbard layer only features a pseudogap
 $\Delta_{\text{pg}} \approx 4$.
All simulations are carried out with the dimensionless factor $\alpha\equiv t_{\text{resc}}E_0/\Omega^{2}<0.5$ for which the FDSA is justified~\footnote{In Ref.~\cite{so.do.18} the factor is defined as $\alpha=t_{c}E_0/\Omega^{2}$ and $t_{\text{c}}=1$. Setting $t_{\text{resc}}=1$, we define for consistency $\alpha$ as in the main text.}. Whenever the electron-phonon interaction is included, we take $g=0.8$ and unless stated otherwise $\omega_{\text{ph}}=0.1$.

@@

\begin{itemize}
\item For $\Omega<\Delta_{\text{pg}}$, 
we expect a strong suppression of the current~\footnote{The remaining leak current originates either from multiple-photon absorption processes
which are strongly suppressed, or from the absence of a true gap.} and
we do not expect any current if the DOS of the correlated layer has a true gap.
\item For $\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$ as shown in Fig.~\ref{fig:energy_setup}(b), an electron coming from the left lead into the LHB is photoexcited to the UHB and can escape directly into the right lead without additional scattering.  Such processes are often referred to as direct excitations (DEs).
\item For $2\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$ as shown in Fig.~\ref{fig:energy_setup}(c), a photoexcited electron in the UHB can excite via II a second electron from LHB to UHB, before both escape into the right lead.
\item For $\Omega>\Delta_{\text{pg}}+2W_{\text{b}}$, there are no final states available for a photoexcited electron and we do not expect the transition to occur. 
\end{itemize}

Notice that in the energy window $\Delta_{\text{pg}}<\Omega<2\Delta_{\text{pg}}$ the only scattering processes taking place are DEs, while for $2\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$, both DE and II can occur. 
This is in contrast to the case of Ref.~\cite{so.do.18}, in which the ad-hoc narrow leads' bands only allow for II processes in a certain $\Omega$-range.
For this reason, and due to the fact that the boundaries of these energy ranges are not strict, it is more difficult to disentangle these physical processes in the present case.

@@

Upon inclusion of e-ph scattering, the outlined scheme remains valid except for the fact that  the pseudogap $\Delta_{\text{pg}}$ is slightly modified. As shown in Sec.~\ref{sec:E0_2_electrons_phonons}, the phonons broaden the DOS of the correlated layer, which slightly fills and shrinks the pseudogap.

\begin{figure*}[t]
\includegraphics[width=0.7\textwidth]{./figures_Paper1/j_vs_omega_mu1_v_0.4_0.8_eph.pdf}
\caption{(Color online) 
 (a) Time-averaged steady state current $j$ and (b) double occupancy $N_{\text{D}}$ plotted as a function of the driving frequency $\Omega$. Results are shown for different values of the lead-layer hybridization $v$ as well as without and with e-ph interaction.
 Default parameters are specified at the beginning of Sec.~\ref{sec:results}.} 
\label{fig:j_vs_omega_mu1_v_0.4_0.8_eph}
\end{figure*}

@@

\begin{figure}[b] 
\includegraphics[width=\linewidth]{./figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_5_11_e.pdf}
\caption{(Color online) Spectral function $A(\omega)$ (solid line) and occupation function $N(\omega)$ (shaded area) at (a) $\Omega=5$ and (b) $\Omega=11$ for $v=0.4$ and $0.8$ for the EO system. Default parameters are specified at the beginning of Sec.~\ref{sec:results}.}
\label{fig:spec_filling_mu1_v_0.4_0.8_O_5_11_e}
\end{figure}

\begin{figure}[b]  
\includegraphics[width=\linewidth]{./figures_Paper1/j_vs_omega_mu1_v_0.8_e_E0_3_4.pdf} 
\caption{(Color online) (a) Time-averaged steady state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, at $v=0.8$ for $E_0=3,4$ for the EO system. Default parameters are specified at the beginning of Sec.~\ref{sec:results}.} 
\label{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4}
\end{figure}

For $\Omega\gtrsim8$, the current increases further until it reaches its peak at $\Omega\approx 11$.
In this range both DE and II can occur in principle. The height of the peak is approximately the same for both $v$, despite both hybridizations differing by a factor of two. The double occupation in this range shows a similar behavior as the current for $v=0.4$ with a peak around $\Omega\approx 11$, while it exhibits a plateau for $v=0.8$. For $v=0.4$ the current curve is characterized by a substantial increase in slope around $\Omega \approx 7$, which cannot be observed for $v=0.8$. This, together with the comparable magnitude of the current maxima at $\Omega\approx 11$ and the behavior of the double occupation strongly suggests that for $v=0.4$ a substantial amount of II processes take place, while these are absent or negligible for $v=0.8$.
Here,  the plateau in $N_{\text{D}}$ for $v=0.8$ suggests that photoexcited electrons arriving in the UHB quickly escape to the right fermionic lead and do not have time to induce II processes.

@@

This behavior is affected by the electric field amplitude $E_0$ as illustrated in Fig.~\ref{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4}(a). For $E_0=4$ the current develops a sudden increase in slope around $\Omega\approx7$, as well as a pronounced peak around $\Omega\approx 11$ for the larger hybridization $v=0.8$. Both features start developing already at $E_0=3$. This tendency, corroborated by the behavior of the double occupation displayed in Fig.~\ref{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4}(b), suggests an  important role of II also for larger values of $v$, provided the field amplitude is strong enough.

@@

The double occupation $N_{\text{D}}$  shown in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b) is larger than and follows the behavior of its EO counterpart within the entire $\Omega$-range considered.
The spectral and occupation functions  shown in Fig.~\ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph} display a redistribution of spectral weight from the peaks towards the edges of the bands, thus reducing the pseudogap. Consequently, the occupation of positive energy states is slightly shifted to the bottom of the UHB compared to the EO case, as the occupation function shows.
 The spectral function in presence of phonons is  broadened and tends to fill the pseudogap $\Delta_{\text{pg}}$ as anticipated in Sec.~\ref{sec:scheme_electrons_phonons}.
This reduction of the pseudogap explains why the current in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a) is slightly larger in presence of phonons for $\Omega\lesssim7$. With a smaller pseudogap and more states at its edges, more electrons can be directly excited with a given driving frequency $\Omega$ thereby increasing the photocurrent. On the other hand, the suppression of the current by e-ph interaction in the range $7\lesssim\Omega\lesssim14$ is due to the dissipation-induced reduction of spectral weight at frequencies $|\omega| \gtrsim 3.5$, see Fig. \ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}.

\begin{figure}[b]
\includegraphics[width=\linewidth]{./figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_11_eph.pdf}
\caption{(Color online) Spectral function $A(\omega)$ (solid line) and occupation function $N(\omega)$ (shaded area) at $\Omega=11$ without and with e-ph interaction, for (a) $v=0.4$ and (b) $v=0.8$. Default parameters are specified at the beginning of Sec.~\ref{sec:results}.} 
\label{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}
\end{figure}

@@

\begin{figure}[t] 
\includegraphics[width=\linewidth]{./figures_Paper1/j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph.pdf}
\caption{(Color online) (a) Time-averaged steady state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, for $v=0.4, 0.8$, at phonon cutoff frequencies $\omega_{\text{ph}}=0.025, 0.05$. Default parameters are specified at the beginning of Sec.~\ref{sec:results}.} 
\label{fig:j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph}
\end{figure}

@@
